surfing

### 2021-05-10 inst/surfing.Rmd
ordertransplot

```{r}
players <- read.table("players.txt",header=TRUE)
head(players)
table(players$nation)
players$name
wildcards <- players$name[-(1:36)]
wildcards
```

@@

@@

>>>>

```{r}
surfing_table <- read.table("wct_surfers_table.txt",header=TRUE)
surfing_table
table(surfing_table$nation)
surfing_table$name
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
```

@@

Test the null of equal strengths:

@@

Now compare the finishing order based on points vs the finishing order
on likelhood:

```{r ordertransplotplot,fig.cap="Official ranks vs likelihood rank, WCT"}
rL <- sort(surfing_maxp,decreasing=TRUE)
rL[] <- seq_along(rL)    # likelihood-based rank
rO <- seq_len(nrow(surfing_table))[1:36]
names(rO) <- rownames(surfing_table)[1:36]
rO
rL
sort(names(rO))
sort(names(rO))
sort(names(rO))==sort(names(rO))
ordertransplot(rO,rL,xlab="offical rank",ylab="likelihood rank",main="WCT 2019")
```
